---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regexcite

<!-- badges: start -->
<!-- badges: end -->

The goal of regexcite is to practice making packages by creating functions to perform common tasks with strings. 

## Installation

You can install the development version of regexcite from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("svs1607/regexcite")
```

## Example

A common task with regular expressions is splitting a string into many parts.This can be done with `base::strplit()` and `stringr::str_split()`.

```{r}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```


These often return a list of length one. For convenience, we wanted an unlisted output and that's what `regexcite::str_split_one()` does.

```{r}
library(regexcite)

str_split_one(x, pattern = ",")
```

`str_split_one()` should only be used when the input is a single string and will error our otherwise.

`str_split_one()` is built on `stringr::str_split()`, so you can use its `n` argument and stringr's general interface for describing the `pattern` to be matched.

```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
